Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems

### 2024-09-25 paper.tex
meeting mit matthias

\documentclass[conference]{resources/IEEEtran}

@@

\begin{document}
	%% TITLE:
	\title{Optimal Task Phasing for End-To-End Latency in Harmonic and Automotive Task Systems}

@@

		% - one sentence detailing your approach (meet the need)
		In this work, we discuss the configuration of task phases to optimize the end-to-end latency of a cause-effect chain.
		% - list main research results
		To that end, we develop a strategy for semi-harmonic task systems, which are very common in industrial applications.
		% - finish with MAIN MESSAGE of the paper
		We prove that our strategy is optimal in the sense that it minimizes the end-to-end latency.
		Furthermore, our evaluation based on a real-world application shows that optimizing task phases can reduce end-to-end latencies significantly. 
	\end{abstract}

@@

\section{Optimal Task Phasing for Automotive Systems}

@@

@@

	- ohne offset
	- random offset
	- unser offset

@@

% bib
\label{last-page}
\clearpage
%\bibliographystyle{abbrv}
%\bibliography{real-time}

>>>>

\documentclass[10pt,conference]{resources/IEEEtran}

@@

\begin{document}
	%% TITLE:
	\title{Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems}

@@

		% - one sentence detailing your approach (meet the need)
		In this work, we discuss the configuration of task phases to optimize the end-to-end latency of a cause-effect chain.
		% - list main research results
		To that end, we develop a strategy for semi-harmonic task systems, which are very common in industrial applications.
		% - finish with MAIN MESSAGE of the paper
		We prove that our strategy is optimal in the sense that it minimizes the end-to-end latency.
		Furthermore, our evaluation based on a real-world application shows that optimizing task phases can reduce end-to-end latencies significantly.

		\mario{11 pages of technical content + bib and ackn; Track 2}
	\end{abstract}

@@

\section{Optimal Task Phasing for Semi-Harmonic Automotive Systems}

@@

	\mario{
	Case Study based on WATERS 2017.

	Synthetic Evaluation based on Automotive Benchmarks for free.
	}

	\mario{Messages: 
	1 Our was always the best (verify optimality)
	2 How much can we gain?
	}

@@

	- ohne phasing
	- random phasing
	- unser phasing

@@

% bib
\label{last-page}
\clearpage
\bibliographystyle{abbrv}
\bibliography{real-time}
